---
title: "Rmarkdown with Plotly"
author: "Aline Riquetti"
date: "3 de outubro de 2017"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## About the data

In a research some data was collect about personal activity relatively inexpensively. In this experiment a group of enthusiasts take measurements about themselves regularly to improve their health, to find patterns in their behavior.

***
- The way the participants perform the experiment was:

1. exactly according to the specification (Class A)
2. throwing the elbows to the front (Class B)
3. lifting the dumbbell only halfway (Class C)
4. lowering the dumbbell only halfway (Class D)
5. hrowing the hips to the front (Class E).

- The measures used was:

1. magnet_dumbbell_x
2. yaw_dumbbell
3. accel_dumbbell_x
4. roll_dumbbel

## Look the data

```{r load_data, echo = FALSE, comment=""}
urlTrain <- "http://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv"
download.file(urlTrain, destfile = "pml-training.csv") 
data <- read.csv("pml-training.csv", na.strings=c("NA","#DIV/0!","")) 
data<-data[c("magnet_dumbbell_x","yaw_dumbbell","accel_dumbbell_x","roll_dumbbell","classe")]
data<-data[sample(nrow(data), round(0.2*nrow(data))), ]
head(data)
```

## 3D plot

```{r plotly, , message=FALSE, warning=FALSE}
library(plotly)
plot_ly(x=data$magnet_dumbbell_x, y=data$yaw_dumbbell, z=data$accel_dumbbell_x, type="scatter3d", mode="markers", color=data$classe, size=data$roll_dumbbel)
```

